Open Set Logo Detection and Retrieval

### 2017-09-01 paper-review.tex
Added classification plot.

The contributions of this work are threefold:
\begin{itemize}
\item A novel open set logo detector which can detect previously unseen logos.
\item An open set logo retrieval system which needs only a single logo image as query.
\item The introduction of a novel in-the-wild logo dataset.
\end{itemize}

@@

\subsection{Detection}
%- train 3 different detectors: multi-class Faster R-CNN (maybe RPN), single-class Faster R-CNN, single-class Faster R-CNN + own logos\\
%- test on FlickrLogos32 => FROC plot\\
%- test first two detectors on own logo dataset => FROC plot\\
%- Example Detections\\
%%TODO write text here
As baseline, the state-of-the-art closed set logo retrieval method from~\cite{??} is employed and trained on the public portion of the training data.
It is adapted to open set detection by using the RPN scores as detections. This skips the closed set classification part of the network which is pre-trained on different logos than should be detected on the test set.
%Because of the closed set training strategy, only brands occurring in the training set are the final outcome of this detector. 
%Adaptation to open set detection of previously unseen logos is achieved by using the RPN scores before classification as detections.
%Because of the strict separation of train and test brands, and the closed set training strategy
%the RPN scores serve as detections.
The proposed logo detector is first trained on the same public data for comparison. The results in figure~\ref{fig:detectionFroc} indicate that this strategy is superior by a significant margin. 
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/detectionFroc.pdf}%
\caption{FROC curve for FlickrLogos32 test set.}%
\label{fig:brandDistribution}
\end{figure}%
%

@@

\subsection{Retrieval}
- train 4 to 6 additional networks: feature extraction network for public and public+own training data --- use VGG16, ResNet50, DenseNet as base network (either for both training sets or only for the public+own)
- results on FlickrLogos32 => FROC plot\\
- results on own sports data => FROC plot\\
%TODO write text here

In addition to public data, target domain specific experiments are performed on TV broadcasts of sports events. In total, 1,218 annotated frames with more than 10,000 logos from four different events are available in our SportLogo dataset where 3 events are used for training and one as test set. Refer to table~\ref{tab:sportDataStatistics} for details. In comparison to public logo datasets, the logos are usually significantly smaller in these cases and cover only a tiny fraction of the image area as illustrated in figure~\ref{fig:footballSample}.
%
\begin{figure*}%
\centering%
\includegraphics[width=\linewidth]{img/football-1908719_1920_cut.jpg}%
\caption{Example football frame with small logos in the perimeter advertising.}%
\label{fig:footballSample}
\end{figure*}%
%

>>>>

The contributions of this work are threefold:
\begin{itemize}
\item A novel open set logo detector which can detect previously unseen logos.
\item An open set logo retrieval system which needs only a single logo image as query.
\item The introduction of a novel large-scale in-the-wild logo dataset.
\end{itemize}

@@

\subsection{Detection}
%- train 3 different detectors: multi-class Faster R-CNN (maybe RPN), single-class Faster R-CNN, single-class Faster R-CNN + own logos\\
%- test on FlickrLogos32 => FROC plot\\
%- test first two detectors on own logo dataset => FROC plot\\
%- Example Detections\\
%%TODO write text here
As baseline, the state-of-the-art closed set logo retrieval method from~\cite{??} is employed and trained on the public portion of the training data.
It is adapted to open set detection by using the RPN scores as detections. This skips the closed set classification part of the network which is pre-trained on different logos than should be detected on the test set.
%Because of the closed set training strategy, only brands occurring in the training set are the final outcome of this detector. 
%Adaptation to open set detection of previously unseen logos is achieved by using the RPN scores before classification as detections.
%Because of the strict separation of train and test brands, and the closed set training strategy
%the RPN scores serve as detections.
The proposed logo detector is first trained on the same public data for comparison. The results in figure~\ref{fig:detectionFroc} indicate that this strategy is superior by a significant margin. 
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/detectionFroc.pdf}%
\caption{Detection FROC curve for FlickrLogos32 test set.}%
\label{fig:detectionFroc}
\end{figure}%
%

@@

\subsection{Retrieval}
%- train 4 to 6 additional networks: feature extraction network for public and public+own training data --- use VGG16, ResNet50, DenseNet as base network (either for both training sets or only for the public+own)
%- describe repeated query logo strategy => 10 sample => mean + std
%- results on FlickrLogos32 => FROC plot\\
%- results on own sports data => FROC plot\\
%%TODO write text here
%
For the retrieval experiments, the state-of-the-art closed set logo retrieval method from the previous section is again used as baseline. The class probabilities are interpreted as feature vector which is then used to match previously unseen logos.
For the proposed open set strategy, the best logo detection network from the previous section is used in all cases. Detected logos are described by the classification network's output feature. Descriptor matching is performed in all cases with cosine similarity. Three different state-of-the-art classification architectures, namely VGG16~\cite{simonyan2014}, ResNet101~\cite{he2015} and DenseNet??~\cite{huang2016}, serve as base for the logo classification stage. All networks are pretrained on ImageNet and afterwards fine-tuned either on the public logo train set or the combination of the public and the Logos in the Wild train data.

In 10 iterations, each of the 10 FlickrLogos32 train samples for each brand serves as query sample. This allows to assess the statistical significance of results similar to a 10-fold-cross-validation strategy. Figure~\ref{fig:classificationFroc} shows the FROC results for the trained networks including indicators for the standard deviation of the measurements. The detection identification rate denotes the amount of ground truth logos which are correctly detected and are assigned the correct brand.
While the baseline is only able to find a minor amount of the logos, our best performing approach is able to correctly retrieve 25 percent of the logos if tolerating only one false alarm every 100 images.
As expected, the more recent network architectures provide better results. Also, including the Logos in the Wild data in the training yields a significant boost in performance. Specifically, the larger training dataset has a larger impact on the performance than a better network architecture. 
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 7cm 0cm 0cm, clip]{img/classificationFroc.pdf}%
\caption{Detection+Classification FROC curve for FlickrLogos32 test set. Including dashed indicators for one standard deviation.}%
\label{fig:classificationFroc}
\end{figure}%
%
%As far as we are aware, this is the first experiment with open set logo retrieval on 
Table~\ref{tab:map} compares our open set results with closed set results from the literature in terms of the mean average precision (map). 
%
\begin{table}[t]
\centering
\begingroup	
\setlength{\tabcolsep}{6pt}
\caption{FlickrLogos32 test set retrieval results.}
\label{tab:sportDataStatistics}
\begin{small}
% Table generated by Excel2LaTeX from sheet 'FlickrLogos32Test'
\begin{tabular}{crc}
\textbf{setting} & \multicolumn{1}{c}{\textbf{method}} & \textbf{map} \bigstrut[b]\\
\hline
\multirow{5}[2]{*}{\begin{sideways}open set\end{sideways}} & baseline~\cite{??} & 0,036 \bigstrut[t]\\
      & VGG16 - public & 0,286 \\
      & ResNet101 - public & 0,327 \\
\cline{2-3}      
      & VGG16 - public+LitW & 0,382 \bigstrut[t]\\
      & ResNet101 - public+LitW & 0,464 \bigstrut[b]\\
\hline
\multirow{5}[1]{*}{\begin{sideways}closed set\end{sideways}} & \cite{??} & ?? \bigstrut[t]\\
      & \cite{??} & ?? \\ %TODO cite values from literature
      & \cite{??} & ?? \\
      & \cite{??} & ?? \\
      & \cite{??} & ?? \\
\end{tabular}%
\end{small}
\endgroup
\end{table}
We achieve ?? percent of the closed set performance with only one sample for a brand at test time instead of dozens or hundreds of brand samples at training time.

In addition to public data, target domain specific experiments are performed on TV broadcasts of sports events. In total, 1,218 annotated frames with more than 10,000 logos from four different events are available in our SportLogo dataset where 3 events are used for training and one as test set. Refer to table~\ref{tab:sportDataStatistics} for details. In comparison to public logo datasets, the logos are usually significantly smaller in these cases and cover only a tiny fraction of the image area as illustrated in figure~\ref{fig:footballSample}.
%
\begin{figure*}%
\centering%
\includegraphics[width=\linewidth]{img/football-1908719_1920_cut.jpg}%
\caption{Example football scene with small logos in the perimeter advertising.}%
\label{fig:footballSample}
\end{figure*}%
%
